plots with prolactin

### 2019-12-03 analysis/16_PRL.Rmd
now with musical prolactin

>>>>

## prolactin manip

```{r PRL.pit.maip}
vsd.pit <- readvsd("../results/06_pitallvsd.csv")
vsd.pit$entrezid <- row.names(vsd.pit)

colData.pit <- read_csv("../metadata/00_samples.csv") %>% 
  filter(tissue == "pituitary") %>% 
  mutate(sample = V1)

geneinfo <- read_csv("../metadata/00_geneinfo.csv") %>%  
  dplyr::select(Name, geneid, entrezid) %>% arrange(Name)

candidategenes <- c("PRL")

candidates.pit <- selectcandidatevsds(candidategenes, vsd.pit, colData.pit)
candidates.pit$treatment <- factor(candidates.pit$treatment, levels = alllevels)

p3 <- ggplot(candidates.pit, aes(x = treatment, y = PRL)) + 
       geom_smooth(aes(colour = sex)) +
    geom_boxplot(aes(fill = treatment)) +
    scale_alpha_manual(values = c(0.75,1)) +
    mytheme() +
   theme(legend.position = "none", legend.direction = "horizontal") + 
   scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
    labs(y = "Pituitary PRL", x = NULL) +
    scale_x_discrete(breaks = c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16)) +
  scale_fill_manual(values = colorscharmaip2) +
  ylim(c(16,22))
p3

meanPRL <- candidates.pit %>% 
    droplevels() %>% 
  dplyr::group_by(treatment) %>%
  dplyr::summarise(m = median(PRL), 
                   se = sd(PRL)/sqrt(length(PRL))) %>%
  dplyr::mutate(m = round(m,1)) 
meanPRL <- left_join(meanPRL, birds)
meanPRL$treatment <- factor(meanPRL$treatment, levels = alllevels)
meanPRL

p4 <- ggplot(meanPRL, aes(treatment, m)) +
   geom_errorbar(aes(ymin=m-se, ymax=m+se, color = treatment), width=.1) +
   geom_image(aes(image = iconpath), size = 0.06)  +
   geom_image(aes(image = music , y = m + 0.5), size = 0.04) +
   labs(x = "parental care stages", y = "Pituitary PRL") +
   mytheme() +
   ylim(c(16,22)) +
   theme(axis.text.x = element_text(angle = 45)) +
  theme(legend.position = "none") +
  scale_color_manual(values = colorscharmaip2) +
  geom_hline(yintercept=16.8) +
  geom_hline(yintercept=17.8) +
  geom_hline(yintercept=18.8) +
  geom_hline(yintercept=19.8) +
  geom_hline(yintercept=20.8) 
p4

```
